\mireval{}

### 2014-05-08 paper/paper.tex
Better goto description
Flattening descriptions

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule (e.g. \mireval{}\texttt{.beat}), and each metric is defined as a separate function in each submodule (e.g. \mireval{}\texttt{.beat.f\char`_measure}).
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}:
The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat;
\textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat;
\textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met;
\textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains;
\textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.

@@

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{} and described below:

\begin{description}
\item[Standard F-measure, Precision, and Recall:] An estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern.
\item[Establishment F-measure, Precision, and Recall:] Computes the number of reference patterns that were successfully found, no matter how many occurrences were found.
      In other words, these metrics capture the ability of the algorithm to \textit{establish} the patterns in a piece.
\item[Occurrence F-measure, Precision, and Recall:] Measures whether an algorithm is able to retrieve all occurrences of a pattern.
      This metric aims to quantize this \textit{occurrence} retrieval quality of the algorithm.
\item[Three-layer F-measure, Precision, and Recall:] These metrics capture both the establishment of the patterns and the occurrence retrieval in a single set of scores.
\item[First $N$ patterns metrics:] The target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance. 
\end{description}

@@

\mireval{} implements the following boundary detection metrics:
\begin{description}
\item[Boundary detection:] precision, recall, and F-measure scores where an estimated boundary is considered correct if it falls within a window around a reference boundary ~\cite{turnbull2007supervised};
\item[Boundary deviation:] median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
\end{description}
and the following structure annotation metrics:
\begin{description}
\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
\item[Rand index:] reference and estimated annotations are sampled uniformly throughout the track, and the induced clusterings are compared by the Rand index ~\cite{rand1971objective};
\footnote{The MIREX results page refers to Rand index as ``random clustering index''.}
\item[Normalized conditional entropy:] reference and estimated labels are sampled uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are computed by estimating the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation})~\cite{lukashevich2008towards}.
\end{description}

\subsection{Melody Extraction}
Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
Melody annotations are represented as time series of fundamental frequency ($f_0$) values in Hz sampled at discrete points (``frames'') in time.
An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
\begin{description}
  \item[Voicing Recall Rate:] The proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm.
  \item[Voicing False Alarm Rate:] The proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm.
  \item[Raw Pitch Accuracy:] The proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency).
  \item[Raw Chroma Accuracy:] As raw pitch accuracy, except that both the estimated and reference $f_0$ sequences are mapped onto a single octave.
  \item[Overall Accuracy:] The proportion of all frames correctly estimated by the algorithm, where for non-melody frames this means the algorithm labeled them as non-melody, and for melody frames the algorithm both labeled them as melody frames and provided a correct $f_0$ estimate for the melody (i.e.~within half a semitone of the reference).
\end{description}
Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.

>>>>

\mireval{} is a Python library which includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions for loading in task-specific data from common file formats.
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source SciPy/Numpy\cite{jones2001scipy} and scikit-learn\cite{pedregosa2011scikit} Python libraries.

@@

\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}:
The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat;
\textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat;
\textbf{Goto's score}, a binary score which is 1 when at least 25\% of the estimated beat sequence closely matches the reference beat sequence;
\textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains;
\textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct;
and finally the \textbf{information gain} of the normalized beat error histogram to a uniform distribution.

@@

Pattern discovery involves the identification of musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
The metrics used to evaluation pattern discovery systems attempt to quantify the ability of the algorithm to not only determine the presents pattern in a piece, but also to find all of their occurrences.
Given the novelty of this task (the first year it appeared in MIREX was 2013), the evaluation metrics are likely to be modified in further editions.
Nonetheless, Collins compiled all previously existent metrics and proposed novel ones \cite{Collins2013}, which resulted in 19 different scores, each one implemented in \mireval{}:
\textbf{Standard F-measure, Precision, and Recall}, where an estimated pattern is considered correct only if it matches (up to translation) a reference prototype pattern;
\textbf{Establishment F-measure, Precision, and Recall}, which computes the number of reference patterns that were successfully found, no matter how many occurrences were found;
\textbf{Occurrence F-measure, Precision, and Recall}, which measures whether an algorithm is able to retrieve all occurrences of a pattern;
\textbf{Three-layer F-measure, Precision, and Recall}, which capture both the establishment of the patterns and the occurrence retrieval in a single set of scores;
and the \textbf{First $N$ patterns metrics}, where the target proportion establishment recall and three-layer precision analyzing the first $N$ patterns only, which measures the ability of the algorithm to sort the identified patterns based on their relevance.

@@

\mireval{} implements the following boundary detection metrics:
\textbf{Boundary detection precision, recall, and F-measure scores} where an estimated boundary is considered correct if it falls within a window around a reference boundary \cite{turnbull2007supervised};
\textbf{Boundary deviation} which computes median absolute time difference from a reference boundary to its nearest estimated boundary, and vice versa \cite{turnbull2007supervised}
The following structure annotation metrics are also included:
\textbf{Pairwise classification precision, recall, and F-measure scores} for classifying pairs of sampled time instants as belonging to the same structural component~\cite{levy2008structural};
\textbf{Rand index}\footnote{The MIREX results page refers to Rand index as ``random clustering index''.} which clusters reference and estimated annotations and compares themby the Rand index ~\cite{rand1971objective};
and the \textbf{Normalized conditional entropy} where sampled reference and estimated labels are interpreted as samples of random variables $Y_R, Y_E$ from which the conditional entropy of $Y_R$ given $Y_E$ (\emph{under-segmentation}) and $Y_E$ given $Y_R$  (\emph{over-segmentation}) are estimated \cite{lukashevich2008towards}.

\subsection{Melody Extraction}

Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
Melody annotations are represented as time series of fundamental frequency ($f_0$) values in Hz sampled at discrete points (``frames'') in time.
An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
\textbf{Voicing Recall Rate} which computes the proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm;
\textbf{Voicing False Alarm Rate} which computes the proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm;
\textbf{Raw Pitch Accuracy} which computes the proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency);
\textbf{Raw Chroma Accuracy} where the estimated and reference $f_0$ sequences are mapped onto a single octave before computing the raw pitch accuracy;
and the \textbf{Overall Accuracy}, which computes the proportion of all frames correctly estimated by the algorithm, including whether non-melody frames where labeled by the algorithm as non-melody.
Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.
